Psp_conjunction

### 2024-01-19 index.qmd
update

@@

@@

[WHPI - Campaign: PSP 15th Perhihelion](https://whpi.hao.ucar.edu/whpi_campaign-psp15p.php)

@@

@@

>>>>

## PSP Encounter Infos

[PSP Science Planning](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters)

| Event | Distance                    | Time                         |
|-------|-----------------------------|------------------------------|
| E1    | 35.6 $R_{\odot}$            | Perihelion: 2018-11-06 03:27 |
| E2    | 35.6 $R_{\odot}$            | Perihelion: 2019-04-04 22:39 |
| E3    | 35.6 $R_{\odot}$            | Perihelion: 2019-09-01 17:50 |
| E4    | 27.8 $R_{\odot}$            | Perihelion: 2020-01-29 09:37 |
| E5    | 27.8 $R_{\odot}$            | Perihelion: 2020-06-07 08:23 |
| E6    | 20.3 $R_{\odot}$            | Perihelion: 2020-09-27 09:16 |
| E7    | 20.3 $R_{\odot}$            | Perihelion: 2021-01-17 17:40 |
| E8    | 0.074 AU (15.9 $R_{\odot}$) | Perihelion: 2021-04-29 08:48 |
| E9    | 15.9 $R_{\odot}$            | Perihelion: 2021-08-09 19:11 |
| E10   | 13.3 $R_{\odot}$            | Perihelion: 2021-11-21 08:23 |
| E11   | 13.3 $R_{\odot}$            | Perihelion: 2022-02-25 15:38 |
| E12   | 13.3 $R_{\odot}$            | Perihelion: 2022-06-01 22:51 |
| E13   | 13.3 $R_{\odot}$            | Perihelion: 2022-09-06 06:04 |
| E14   | 13.3 $R_{\odot}$            | Perihelion: 2022-12-11 13:16 |
| E15   | 13.3 $R_{\odot}$            | Perihelion: 2023-03-17 20:30 |
| E16   | 13.3 $R_{\odot}$            | Perihelion: 2023-06-22 03:46 |
| E17   | 11.4 $R_{\odot}$            | Perihelion: 2023-09-27 23:28 |
| E18   | 11.4 $R_{\odot}$            | Perihelion: 2023-12-29 00:54 |
| E19   | 11.4 $R_{\odot}$            | Perihelion: 2024-03-30 02:20 |
| E20   | 11.4 $R_{\odot}$            | Perihelion: 2024-06-30 03:46 |
| E21   | 11.4 $R_{\odot}$            | Perihelion: 2024-09-30 05:13 |
| E22   | 9.9 $R_{\odot}$             | Perihelion: 2024-12-24 11:41 |
| E23   | 9.9 $R_{\odot}$             | Perihelion: 2025-03-22 22:25 |
| E24   | 9.9 $R_{\odot}$             | Perihelion: 2025-06-19 09:09 |

@@

## Trange: Encounter 8

@@

-   [WHPI - Campaign: PSP 8th Perhihelion](https://whpi.hao.ucar.edu/whpi_campaign-psp8p.php)
-   [WHPI - Campaign: PSP 15th Perhihelion](https://whpi.hao.ucar.edu/whpi_campaign-psp15p.php)

@@

![](images/paste-2.png)

@@

## Trange

> C4, 18 September, b 2021. This will be an inferior triple SO–PSP–STEREO-A conjunction, with SO inside the orbit of Venus around 0.6 AU, PSP at about 0.7 AU, and STEREO-A at 0.9 AU. This will be an occasion for joint in situ studies of the properties of turbulence and dynamics of a solar wind stream between 0.5 and 1 AU.

https://solar-mach.streamlit.app/?embedded=true&date=20210925&time=0000&coord_sys=0&plot_spirals=1&plot_sun_body_line=1&plot_trans=0&plot_markers=Numbers&long_offset=270&bodies=STEREO+A&bodies=Earth&bodies=BepiColombo&bodies=Parker+Solar+Probe&bodies=Solar+Orbiter&speeds=346&speeds=485&speeds=400&speeds=300&speeds=287&

![](images/paste-8.png)

![](images/paste-9.png)

![](images/paste-7.png)

![](images/paste-6.png)

![](images/paste-10.png)

::: {.column-page layout-nrow="1"}
![](https://www.ngdc.noaa.gov/dscovr/plots/dscovr_3day_plots/2021/20210802-3day.png)

![](https://www.ngdc.noaa.gov/dscovr/plots/dscovr_3day_plots/2021/20210805-3day.png)
:::

## Trange: Encounter 11, 2022-02

> E11, C6, Q8, Q9 23–27 February, 2022. PSP approaches encounter E11 beginning with a trailing quadrature Q8 on 23 February, 2022, appearing on the east limb of the Sun from SO, before rapidly going through conjunction with STEREO-A and then SO and Earth (24 and 25 February, respectively) at perihe- lion with the Earth–Sun–STEREO-A angle '40◦ and the Earth–

![](images/paste-3.png)

[![](images/paste-4.png)](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E11_HEE.png)

![](images/paste-5.png)

::: {.column-page layout-nrow="1"}
![](https://www.ngdc.noaa.gov/dscovr/plots/dscovr_3day_plots/2022/20220225-3day.png)

![](https://www.ngdc.noaa.gov/dscovr/plots/dscovr_3day_plots/2022/20220228-3day.png)
:::
